Initial Analysis

### 2019-11-11 Initial_Analysis.Rmd
Updates to stauts plot for Vicky analysis

Spp <- 601417

EstSppStatus <- function(Spp,Coord){

  # Load species' data
  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
    set_names(c(seq(1950,2014,1),"INDEX","Species","Longitude","Latitude")) %>% 
    gather("Year","Value",`1950`:`2014`) %>%
    arrange(INDEX) %>% 
    left_join(Index_Code,
              by = "INDEX") %>% 
    filter(!is.na(EEZID),
           Value > 0) %>% 
    group_by(TaxonKey=Species,Year,Territory) %>% # Estimates total catch per country
    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
    group_by(TaxonKey,Territory,Year) %>% # Running mean as Pauly et la.
    mutate(RMean = rollmean(x = Total_Catch, 3,
                            align = "right",
                            fill = Total_Catch)
    ) %>% 
    select(-Total_Catch) %>% 
    ungroup() %>% 
    mutate(Year = as.numeric(Year))

@@

  # Determine the final status using the top category over the last 10 years
  Determine_Status_Data <- Status_Data %>% 
    filter(Year > 2004) %>% # last 10 years of data (2005-2014)
    group_by(TaxonKey,Territory,Status) %>%
    summarise(n_Status= n()) %>%
    group_by(TaxonKey,Territory) %>%
    top_n(1,n_Status)

@@

  # In this case we sue the last year's category
  Duplicates_Status <- Status_Data %>% 
  filter(Territory %in% Duplicates,
         Year == 2014) %>%
    ungroup() %>%
    select(TaxonKey,Territory,Status)

@@

  # Function Return

@@

  # If only No status data, then just return No Status Data
  if(nrow(No_Status_Data) > 0 & nrow(Final_Status_Data) == 0){
    return(No_Status_Data)
  }else{
    return(Final_Status_Data)
  }
}

>>>>

# Spp <- 601417

EstSppStatus <- function(Spp,Coord,Save_Path = "NA", Per_Taxa = F){

  # Load species' data
  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
    set_names(c(seq(1950,2014,1),"INDEX","Species","Longitude","Latitude")) %>% 
    gather("Year","Value",`1950`:`2014`) %>%
    arrange(INDEX) %>% 
    left_join(Index_Code, # Match species catch with INDEX
              by = "INDEX") %>% 
    filter(!is.na(EEZID),
           Value > 0) %>% 
    group_by(TaxonKey=Species,Year,Territory) %>% # Estimates total catch per country
    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
    group_by(TaxonKey,Territory,Year) %>% # Running mean as Kleisner & Pauly 2012
    mutate(RMean = rollmean(x = Total_Catch, 3,
                            align = "left",
                            fill = Total_Catch)
    ) %>% 
    select(-Total_Catch) %>% 
    ungroup() %>% 
    mutate(Year = as.numeric(Year))

@@

  #_______________#
  # Function Return 
  #_______________#

  ### Save the data for each species in all years if Per_taxa = T

  if(Per_Taxa == T){

    Save_path <- NA

    if(is.na(Save_path) == TRUE){

      Save_Path <- Results_Path # standar result's path in my Drobo
    }

    # File name for each species
    Name <- paste(Save_Path,"Stock_Status/",Spp,"_Status.csv",sep="")

    # Save file for each species
    write_csv(Status_Data,
              Data_Name)
  }else{

    ### Determine the final status using the top category over the last 10 years

    Determine_Status_Data <- Status_Data %>% 
      filter(Year > 2004) %>% # last 10 years of data (2005-2014)
      group_by(TaxonKey,Territory,Status) %>%
      summarise(n_Status= n()) %>%
      group_by(TaxonKey,Territory) %>%
      top_n(1,n_Status)

@@

    # In case we have a tide, we use the last year's category
    Duplicates_Status <- Status_Data %>% 
      filter(Territory %in% Duplicates,
             Year == 2014) %>%
      ungroup() %>%
      select(TaxonKey,Territory,Status)

@@

@@

    # If only No status data, then just return No Status Data
    if(nrow(No_Status_Data) > 0 & nrow(Final_Status_Data) == 0){
      return(No_Status_Data)
    }else{
      return(Final_Status_Data)
    }
  } # close if per taxa
}
